Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-15 paper.tex
update bibliography w bibtex

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_RDCL2019}
{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}

\bibitem{ref_tobacco800}
{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}

\bibitem{ref_icdar}
{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}

\bibitem{ref_NoisyOffice}
{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}

\bibitem{ref_NoisyOfficeDatabase}
{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}

\bibitem{ref_UCIMLR}
{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}

\bibitem{ref_fastai}
{Jeremy Howard and Sylvain Gugger, Fastai: A Layered API for Deep Learning. Information 2020, 2, 11}

\bibitem{ref_albumentations}
{Alexander Buslaev, Vladimir I. Iglovikov, Eugene Khvedchenya, Alex Parinov, Mikhail Druzhinin, and Alexandr A. Kalinin. Albumentations: Fast and flexible image augmentations. Information, 11(2), 2020.}

\bibitem{ref_imgaug}
  {Alexander B. Jung, Kentaro Wada, Jon Crall, Satoshi Tanaka, Jake Graving, Christoph Reinders, Sarthak Yadav, Joy Banerjee, Gabor Vecsei, Adam Kraft, Zheng Rui, Jirka Borovec, Christian Vallentin, Semen Zhydenko, Kilian Pfeiffer, Ben Cook, Ismael Fernandez, Francois-Michel De Rainville, Chi-Hung Weng, Abner Ayala-Acevedo, Raphael Meudec, Matias Laporte, et al. imgaug. https://github.com/aleju/imgaug, 2020. Online; accessed 01-Feb-2020.}
\end{thebibliography}
\end{document}

>>>>

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{paper}

\end{document}
